Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-13 docs/ms.tex
Update ms.tex

Finally we can add noise on $\epsilon_{\ell}$ to get the
observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
the situation when P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.

@@

We show the posterior samples of both g and $\alpha$, for both beta
function and step function model.

>>>>

Finally we can add noise on $\epsilon_{\ell}$ to get the
observed ellipticity $\epsilon_{ob}$. For simplicity we've only considered
the situation where P($\epsilon_{ob}|\epsilon_{\ell})$ is a 2D Gaussian.

@@

We show the posterior samples of both $g$ and $\vec{\alpha}$, for both beta
function and step function model.
